Highly Available Transactions: Virtues and Limitations

### 2013-04-01 writeup/evaluation.tex
fixed

\vspace{.5em}\noindent\textbf{Non-serializability} Many existing
distributed implementations of weak isolation are not highly
available. Lock-based proposals such as those used to provide weak
isolation in Gray's original proposal~\cite{gray-isolation} do not
degrade gracefully in the presence of partial failure. (Note, however,
that lock-based protocols \textit{do} offer the benefit of recency
guarantees.) While multi-versioned storage systems allow for a variety
of transactional guarantees, we have not seen proposals for truly weak
isolation (e.g., non-``tentative update'' schemes) in this context.
The MDCC~\cite{mdcc} protocol offers Read Committed isolation with
Lost Update avoidance but is similarly unavailable due to its reliance
on preventing write conflicts. Chan and Gray's read-only transactions
provide read-only transactions with item-cut isolation, causal
consistency, and transactional atomicity (session PL-2L~\cite{adya})
but are unavailable in the presence of coordinator
failure~\cite{readonly}, similar to read-only and write-only
transactions more recently proposed by Eiger~\cite{eiger}; Causal
Serializability offers a similar model (with unavailable
implementation): causal consistency with a variant of Read Uncommitted
between transactions that write to the same data
item~\cite{raynal-causal}.  Bolt-on causal consistency~\cite{bolton},
Brantner's S3 database~\cite{kraska-s3}, and
Bayou~\cite{sessionguarantees} can all provide variants of session
PL-2L with high availability, but none provide this HAT functionality
without substantial modification; Swift~\cite{swift} is closest to
providing full HAT operation in a sticky context. As we have seen, it
is possible to implement many guarantees weaker than
serializability---including guarantees that are achievable with high
availability---and still not achieve high availability.

>>>>

\vspace{.5em}\noindent\textbf{Non-serializability} Many existing
distributed implementations of weak isolation are not highly
available. Lock-based proposals such as those used to provide weak
isolation in Gray's original proposal~\cite{gray-isolation} do not
degrade gracefully in the presence of partial failures. (Note, however,
that lock-based protocols \textit{do} offer the benefit of recency
guarantees.) While multi-versioned storage systems allow for a variety
of transactional guarantees, we have not seen proposals for truly weak
isolation (e.g., non-``tentative update'' schemes) in this context.
The MDCC~\cite{mdcc} protocol offers Read Committed isolation with
Lost Update avoidance but is similarly unavailable due to its reliance
on preventing write conflicts. Chan and Gray's read-only transactions
provide read-only transactions with item-cut isolation, causal
consistency, and transactional atomicity (session PL-2L~\cite{adya})
but are unavailable in the presence of coordinator
failure~\cite{readonly}, similar to read-only and write-only
transactions more recently proposed by Eiger~\cite{eiger}; Causal
Serializability offers a similar model (with unavailable
implementation): causal consistency with a variant of Read Uncommitted
between transactions that write to the same data
item~\cite{raynal-causal}.  Bolt-on causal consistency~\cite{bolton},
Brantner's S3 database~\cite{kraska-s3}, and
Bayou~\cite{sessionguarantees} can all provide variants of session
PL-2L with high availability, but none provide this HAT functionality
without substantial modification; Swift~\cite{swift} is closest to
providing full HAT operation in a sticky context. As  seen, it
is possible to implement many guarantees weaker than
serializability---including guarantees that are achievable with high
availability---and still not achieve high availability.
